---
title: "Extracting COVID Data for Tableau"
author: "Jay Bhushan"
output: html_notebook
---

Get the data from https://ourworldindata.org/covid-deaths.

1. Import data and have a look.


```{r}

data <- read.csv("owid-covid-data.csv", header=TRUE)

str(data)

```
2. I want to start with Total Cases, Total Deaths and Death Percent across all countries.

```{r}


total_cases <- sum(data$new_cases, na.rm=TRUE)
total_deaths <- sum(data$new_deaths, na.rm=TRUE)

death_percent <- (total_deaths/total_cases)*100


df1 <- data.frame(total_cases, total_deaths, death_percent)
```

3. Now I want to look at total deaths per region, specifically - Europe, North America, South America, Asia, Africa and Oceania. 

```{r}
unique(data$continent)


Asia <- sum(data[data$continent=="Asia", ]$new_cases, na.rm = TRUE)
Europe <- sum(data[data$continent=="Europe", ]$new_cases, na.rm = TRUE)
Africa <- sum(data[data$continent=="Africa", ]$new_cases, na.rm = TRUE)
North_America <- sum(data[data$continent=="North America", ]$new_cases, na.rm = TRUE)
South_America <- sum(data[data$continent=="South America", ]$new_cases, na.rm = TRUE)
Oceania <- sum(data[data$continent=="Oceania", ]$new_cases, na.rm = TRUE)

df2 <- data.frame(Asia, Europe, Africa, North_America, South_America)
df2.names <- c("Asia", "Europe", "Africa", "North America", "South America")

```

4. Now let's look country specific. I'll go for Country, Population, Highest Number of Cases, Maximum Percent of Population Infected 

```{r}



df3 <- aggregate(new_cases ~ location + population, data, sum)


```



Export data for use in Tableau 
```{r}
write.csv(df1, file="Tableau Table 1.csv", row.names=FALSE)
write.csv(df2, file="Tableau Table 2.csv", row.names=FALSE)
```

